---
title: "HW_2"
author: "Antonietta"
date: "2/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages}
# packages to be used
library(gapminder)
library(tidyverse)
```

# Exercise 1 : Basic dplyr

## Task 1: filter () subset gapminder  data to 3 countries; France, Japan, and Italy and pipe %>% to select country and gdpPercap 

```{r}
gapminder %>%
  select(country, year, gdpPercap) %>%
  filter(country %in% c ("France" , "Japan", "Italy"), year == "1970":"1979")

```
           
## Task 2: Make new variable for the change life expectancy to show they have dropped 

```{r}
gapminder %>%
  mutate (droplifeExp = lag(lifeExp))

``` 


## Task3: filter gapminder to show max GDP per cap by each country
```{r}
gapminder %>%
  select(country, gdpPercap) %>%
  mutate(gdpPercap_max = gdpPercap) %>%
  group_by(country) %>%
  filter(gdpPercap_max == max(gdpPercap_max))
```


## Task 4: Produce scatterplot of Canada's life expectancy vs GDP

```{r}
gapminder %>%
  filter(country == "Canada") %>%
  ggplot() +
  aes(x =lifeExp, y = gdpPercap) +
  geom_point(fill = "green" , color = "green", alpha = .5 , size = 2) +
  scale_y_continuous(trans = 'sqrt')


```


# Exercise 2 : Explore 2 variables with dplyr and ggplot2 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

``` {r load packages}

# packages to be used
library(palmerpenguins)
library(gapminder)
library(ggplot2)

```

## Task 1: Quantitative variables 
Summary of descriptive statistics and scatterplot 
The variables used are; flipper length and body mass of the penguins 

```{r summary}
palmerpenguins::penguins %>%
    summarize(mu_length = mean(flipper_length_mm, na.rm = TRUE) , 
                          mu_weigth = mean(body_mass_g, na.rm = TRUE))

ggplot(palmerpenguins::penguins) +
aes(x = body_mass_g ,
    y = flipper_length_mm) +
geom_point(fill = "purple" , color = "purple", alpha = .5 , size = 1, shape = 23)
```



## Task 2: Categorical variable and Quantitative variable 
Make summary and useful plots to visualize these variables 
The variables used are flipper length and sex of the penguins 

``` {r}

group_by(penguins , flipper_length_mm, sex) %>% 
summarise(
  count = n(), 
  mean = mean(flipper_length_mm, na.rm = TRUE),
  sd = sd(flipper_length_mm, na.rm = TRUE))%>% 
  ungroup()

ggplot(palmerpenguins::penguins) +
  aes(x = sex , 
      y = flipper_length_mm ,
      fill = sex, 
      color = sex) +
  geom_jitter(height = 0 , 
              width = .4) 


```




# Bonus Exercise: Evaluate this code and describe the result. The goal was to get the data for Rwanda and Afghanistan. Does this work? Why or why not? If not, what is the correct way to do this?

``` {r}
filter(gapminder, country == c("Rwanda", "Afghanistan"))

```

The previous code is filtering gapminder and countries to include Rwanda and Afghanistan, however, a more efficient way to do this is using gapminder and piping '%>%', which means 'and then...' to filter the countries by using '%in%' instead of '=='. '%in%' has a similar property than '==' except that it checks the input values against all the other values in the vector.  


``` {r}
gapminder %>%
filter(country %in% c("Rwanda", "Afghanistan"))

```




