---
title: "HW_2"
author: "Antonietta"
date: "2/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages}
# packages to be used
library(gapminder)
library(tidyverse)
```

# Exercise 1 : Basic dplyr

## Task 1: filter () subset gapminderl data to 3 countries; France, Japan, and Italy and pipe %>% to select country and gdpPercap 

```{r}
gapminder %>%
  select(country, year, gdpPercap) %>%
  filter(country %in% c ("France" , "Japan", "Italy"), year == "1970":"1979")

```
           
## Task 2: Make new variable for the change life expectancy to show they have dropped 

```{r}
gapminder %>%
  mutate (droplifeExp = lag(lifeExp))

``` 


## Task3: filter gapminder to show max GDP per cap by each country
```{r}
gapminder %>%
  select(country, gdpPercap) %>%
  mutate(gdpPercap_max = gdpPercap) %>%
  group_by(country) %>%
  filter(gdpPercap_max == max(gdpPercap_max))
```


## Task 4: Produce scatterplot of Canada's life expectancy vs GDP

```{r}
gapminder %>%
  filter(country == "Canada") %>%
  ggplot() +
  aes(x =lifeExp, y = gdpPercap) +
  geom_point(fill = "green" , color = "green", alpha = .5 , size = 2) +
  scale_y_continuous(trans = 'sqrt')


```


# Exercise 2 : Explore 2 variables with dplyr and ggplot2 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

``` {r load packages}
# packages to be used
library(palmerpenguins)
library(gapminder)
library(ggplot2)

```

## Task 1: Quantitative variables 
Summary of descriptive statistics and scatterplot 













