---
title: "HW_1_Data_Exploring"
author: "Antonietta"
date: "1/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exploring Markdown

On this project I will be exploring _palmerpenguins_ dataset. We will focus on exploring the body mass of penguins. 


### Part 1 

We will begin by exploring the general summary of the dataset. 

```{r summary} 

library(palmerpenguins)

summary(penguins)

head(penguins)

nrow(penguins)

```

We can see that the penguin's *body mass* _mean_ was 4202 grams, with the lowest body mass at 2700 grams and the highest at 6300 grams. 




### Part 2 


On this section we will explore the body mass of the penguins, looking at a *histogram* for normal distribution, a *boxplot* for homogenity of variance, and a *plot* graph. 


```{r graphs}
hist(penguins$body_mass_g)
boxplot(penguins$body_mass_g)
plot(penguins$body_mass_g)

```

From the histogram and boxplot we can see that the penguin's body mass was slightly right skewed. 

#END OF THE DATA EXPLORATION 



