---
title: "Final Project"
author: "Antonietta"
date: "5/3/2021"
output: 
  html_document: default
  github_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(ggdist)
```

```{r data, setup, include=FALSE}

if (!dir.exists(here::here("FP", "data"))) {
  dir.create(here::here("FP", "data"), recursive = TRUE)
}
covid_data <- read_csv(here::here("FP", "data", "prison_covid.csv"),
                       na = c("", "NaN", "Inf", "-Inf", "NA"))
pop_data <- read_csv(here::here("FP", "data", "prison_populations.csv"),
                     na = c("", "NaN", "Inf", "-Inf", "NA"))
staff_data <- read_csv(here::here("FP", "data", "staff_populations.csv"),
                       na = c("", "NaN", "Inf", "-Inf", "NA"))
```


# The data: 

For this project, I will only be looking at prisons COVID-19 rates for the state of New York; I will  be looking at the total prisoners cases, and deaths compared to recovery. I will also be looking at the total number of staffs' cases, which could have let to high number of prisoner's cases. 
 
We will be filtering the data set so that it includes only the variables of interest.

```{r}
ny_cases <- covid_data %>%
  filter(name == "New York") %>%
  select(total_prisoner_cases, total_prisoner_deaths, prisoners_recovered, total_staff_cases, as_of_date)
```


# Summary of simple statistics for the variables of interest. 

```{r}
ny_cases %>%
  group_by(total_prisoner_cases, total_prisoner_deaths) %>%
  summarise(across(c(total_staff_cases),
    list(
      mean = ~ mean(.x, na.rm = TRUE),
      sd = ~ sd(.x, na.rm = TRUE),
      min = ~ min(.x, na.rm = TRUE),
      max = ~ max(.x, na.rm = TRUE))))
```
    

# Main plot: this plot looks at the tootal cases of COVID-19 in New York prisoners 


```{r}
main_plot <- ny_cases %>%
  ggplot(aes(x = as_of_date,
      y = total_prisoner_cases)) + 
  geom_point(alpha= 5, 
             shape= 20,
             color="#C8A2C8",
        fill= "#C8A2C8") +
  scale_y_continuous("Prisoners COVID-19 Cases") +
  scale_x_discrete("Date") +
  ggtitle("New York Prisoners' COVID-19 Cases") +
  theme_light()


main_plot
```



# Staff & Prisoners plot: this plot looks at the total cases of COVID-19 in New York prisoners as well as the total cases of COVID-19 in the prison's staff 


```{r}
staff_prisonersplot <- ny_cases %>%
  ggplot(aes(x = total_staff_cases,
      y = total_prisoner_cases)) + 
  geom_point(alpha= 5, 
             shape= 20,
             color="#C8A2C8",
        fill= "#C8A2C8") +
  geom_smooth(method = "loess") +
  scale_y_continuous("Prisoners COVID-19 Cases") +
  scale_x_discrete("Prison Staff COVID-19 Cases") +
  ggtitle("New York Prisoners' COVID-19 Cases") +
  theme_light()

staff_prisonersplot
```


# Staff & Prisoners plot: this plot looks at the total cases of COVID-19 in New York prisoners as well as the total number of recovered prisoners 

```{r}
prisoners_recoveryplot <- ny_cases %>%
  ggplot(aes(x = total_prisoner_cases,
      y = prisoners_recovered)) + 
  geom_point(alpha= 5, 
             shape= 20,
             color="#C8A2C8",
        fill= "#C8A2C8") +
  geom_smooth(method = "loess") +
  scale_y_continuous("Prisoners COVID-19 Cases") +
  scale_x_discrete("Prisoners Recovered") +
  ggtitle("New York Prisoners' COVID-19 Cases") +
  theme_light()

prisoners_recoveryplot
```

# Staff & Prisoners plot: this plot looks at the total cases of COVID-19 in New York prisoners as well as the total number of recorded prisoner's death by COVID-19

```{r}
prisoners_deathplot <- ny_cases %>%
  ggplot(aes(x = total_prisoner_cases,
      y = total_prisoner_deaths)) + 
  geom_point(alpha= 5, 
             shape= 20,
             color="#C8A2C8",
        fill= "#C8A2C8") +
  geom_smooth(method = "loess") +
  scale_y_continuous("Prisoners COVID-19 Cases") +
  scale_x_discrete("Prisoners Death by COVID-19") +
  ggtitle("New York Prisoners' COVID-19 Cases") +
  theme_light()

prisoners_deathplot
```
