---
title: "HW_2"
author: "Antonietta"
date: "2/6/2021"
output:   
  html_document: default
  github_document: default
  keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gapminder)
library(tidyverse)
library(palmerpenguins)
library(gapminder)
library(ggplot2)

```


# Exercise 1 : Basic dplyr

## Task 1: filter () subset gapminder  data to 3 countries; France, Japan, and Italy and pipe %>% to select country and gdpPercap 

We will be piping using '%>%' to tell R in what order to perform the functions 
We will use filter() to have R return the rows that match our select condition of country 
We will then us %in% so it checks all of our input values against each other
Our input values will come from a vector that we will create with the function c() 
We will select the decade of the 70s by adding year>1969 & year <1980 into the filter section 
Finally we will use the function select () to take the subset of country , year and GDP from the  gapminder


```{r filter , echo=FALSE}
gapminder %>%
  filter(country %in% c ("France" , "Japan", "Italy"), year>1969 & year <1980) %>%
  select(country, year, gdpPercap) 

```
           
## Task 2: Make new variable for the change life expectancy to show they have dropped 

We will pipe from gapminder
We will mutate the lifeExp variable, which creates a new variable named droplifeExp
In the mutation we will add the function lag() to our original object to shift the time back 

```{r mutate , echo=FALSE}
gapminder %>%
  mutate (droplifeExp = lag(lifeExp))

``` 


## Task 3: filter gapminder to show max GDP per cap by each country

We will pipe from gapminder 
Once again we will use the function select() to take the substes of country and GDP
We will mutate the gdpPercap object in order to have a new object that represents the highest GDP per cap
We will group by country, so it shows max GDP for each country
We will filter gdpPercap_max and use the max() function to show only the max GDP per cap

```{r max, echo=FALSE}
gapminder %>%
  select(country, gdpPercap) %>%
  mutate(gdpPercap_max = gdpPercap) %>%
  group_by(country) %>%
  filter(gdpPercap_max == max(gdpPercap_max))
```

## Task 4: Produce scatterplot of Canada's life expectancy vs GDP

We will pipe from gapminder
We will use filter () so R returns the row that matches our variable 
We will then pipe to ggplot 
We will use aes() to compute our x and y variables 
We will use geom_point to compute for our plot's visuals 
We will use scale_y_continuous to present the y axis in log of 10 


```{r scatterplot , echo=FALSE}
gapminder %>%
  filter(country == "Canada") %>%
  ggplot() +
  aes(x =lifeExp, y = gdpPercap) +
  geom_point(fill = "green" , color = "green", alpha = .5 , size = 2, shape = 23) +
  scale_y_continuous(trans = 'log10')


```


# Exercise 2 : Explore 2 variables with dplyr and ggplot2 


## Task 1: Quantitative variables 
Summary of descriptive statistics and scatterplot 
The variables used are; flipper length and body mass of the penguins 

We employ summarize() so R gies us a new data frame where our rows will be combined into one 
We wll use ggplot() int he same way as Exercise 1 Task #4 

```{r summary , echo=FALSE}
palmerpenguins::penguins %>%
    summarize(mu_length = mean(flipper_length_mm, na.rm = TRUE) , 
                          mu_weigth = mean(body_mass_g, na.rm = TRUE))

ggplot(palmerpenguins::penguins_raw) +
aes(x = `Body Mass (g)`, y = `Flipper Length (mm)`) +
geom_point(fill = "purple" , color = "purple", alpha = .5 , size = 1, shape = 23)
```



## Task 2: Categorical variable and Quantitative variable 
Make summary and useful plots to visualize these variables 
The variables used are flipper length and sex of the penguins 

We will use the function group_by() to then summarise the specific rows we previously grouped 
We will ungroup() 
We will use ggplot() as we had done before, but this time adding geom_jitter() to add random variability and solve overplotting 

``` {r summarise , echo=FALSE}

group_by(penguins , flipper_length_mm, sex) %>% 
summarise(
  count = n(), 
  mean = mean(flipper_length_mm, na.rm = TRUE),
  sd = sd(flipper_length_mm, na.rm = TRUE))%>% 
  ungroup()

ggplot(palmerpenguins::penguins_raw) +
  aes(x = Sex , 
      y =`Flipper Length (mm)`,
      fill = Sex, 
      color = Sex) +
  geom_jitter(height = 0 , 
              width = .4) 

```




# Bonus Exercise: Evaluate this code and describe the result. The goal was to get the data for Rwanda and Afghanistan. Does this work? Why or why not? If not, what is the correct way to do this?

``` {r bonus , echo=FALSE}
filter(gapminder, country == c("Rwanda", "Afghanistan")) 

```

The previous code is filtering gapminder and countries to include Rwanda and Afghanistan, however, a more efficient way to do this is using gapminder and piping '%>%', which means 'and then...' to filter the countries by using '%in%' instead of '=='. '%in%' has a similar property than '==' except that it checks the input values against all the other values in the vector.  


``` {r answer, echo=FALSE }
gapminder %>%
filter(country %in% c("Rwanda", "Afghanistan"))

```




