---
title: "HW_3"
author: "Antonietta"
date: "2/23/2021"
output:   
  github_document: default
  html_document: default
---

<!-- BMW: Please knit your documents twice. Once to github_document format and once to html_document format. Don't use the keep_md option. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr) 
library(ggplot2)
library(tidyverse) # BMW: library(tidyverse) already loads dplyr and ggplot2, you don't need both.
library(scales)
library(knitr) # BMW: Why are you loading knitr? 
```

# Homework 03

You will analyze data looking at the relationship between **green reputation** and three personality traits--**compassion**, **intellectual curiosity**, and **openness to experiences**.
The dataset includes data from **students** and **non-students**.

```{r}
dictionary <- readr::read_csv("green_dictionary.csv")
green_data <- readr::read_csv("green_data.csv")
``` 

For your assignment, do the following.

  1. Inspect the item responses (e.g., with graphs or by summarizing distinct values). 
     Is anything unusual?
     
<!-- BMW: You need a blank link between text and code chunks. -->
     
```{r}
print(green_data)  #The -99 is unusual

reversed <- dictionary %>%
  filter(Keying == -1) %>%
  pull(Item)

new_green_data <- green_data %>%
  mutate(across(everything(),
                ~ na_if(.x , "-99")))

#The min. value of -99 is now replaced with 1, and all the -99 are NA

summary(new_green_data) # BMW: Generally avoid the summary() command. Compute a more compact table, such as using summarize()

#   ~ says that you are going to use the .x symbol , .x marks the spot
# 'everything()' = ALL COLUMNS
# .missing is for when you look for missing values
# NA is for when this is missing
# .x = the current column 
```


  2. Compute total scores for the four scales. 
     Recode variables as needed.
     
```{r recoding}
#We will be recoding variables to make them more concrete and easier to read

new_green_data %>%
  rowwise() %>%
  mutate(
    green_tot = sum(c_across(green1:green5), na.rm = TRUE),
    comp_tot = sum(c_across(comp1:comp10), na.rm = TRUE),
    intel_tot = sum(c_across(intel1:intel10), na.rm = TRUE),
    open_tot = sum(c_across(open1:open10), na.rm = TRUE)
  )

print(new_green_data)
```   


  3. Rescale the variables so that they go from 0-100 instead of the original range.
     Name the rescaled variables `*_pomp`.
```{r , rescaling variables}
ng_data <- new_green_data %>%
  mutate(across(
    c(green1:open10),
    ~ recode(
      .x,
      "1" = 0,
      "2" = 25,
      "3" = 50,
      "4" = 75,
      "5" = 100
    ),
    .names = "{.col}_pomp"
  ))

ng_data <- ng_data %>%
  rowwise() %>%
  mutate(
    green_tot_pomp = mean(c_across(green1_pomp:green5_pomp), na.rm = TRUE),
    comp_tot_pomp = mean(c_across(comp1_pomp:comp10_pomp), na.rm = TRUE),
    intel_tot_pomp = mean(c_across(intel1_pomp:intel10_pomp), na.rm = TRUE),
    open_tot_pomp = mean(c_across(open1_pomp:open10_pomp), na.rm = TRUE)
  ) %>% 
  ungroup() # BMW: Always ungroup() after using group_by() or rowwise()

ng_data$student <-
  recode_factor(ng_data$student,
                "1" = "not a student",
                "2" = "student") # BMW: NA_character_, not NULL, but you can also omit--it will be NA if there is no match.

print(ng_data) # BMW: Don't print out whole datasets in your final script.
```




  4. Make plots that illustrate the distributions of the 4 POMP-scored variables.

```{r plots}
ggplot(ng_data) +
  aes(green_tot_pomp) +
  geom_histogram(fill = "pink" ,
                 col = "black") +
  theme_classic()

ggplot(ng_data) +
  aes(intel_tot_pomp) +
  geom_histogram(binwidth = 5 ,
                 fill = "orange",
                 col = "black") +
  theme_classic()

ggplot(ng_data) +
  aes(comp_tot_pomp) +
  geom_histogram(binwidth = 5,
                 fill = "cyan",
                 col = "black") +
  theme_classic()

ggplot(ng_data) +
  aes(open_tot_pomp) +
  geom_histogram(binwidth = 5,
                 fill = "violet",
                 col = "black") +
  theme_classic()
```  

The histograms show that all the variables are roughly normally distributed. The green reputation total variable seems to be slightly negatively skewed. 



  5. Make scatterplots showing the relationships between **green reputation** and each personality trait.
     Include trend lines for **students** and **non-students**.
     What do these plots show?
     
```{r, scatterplots}
ggplot(na.omit(ng_data)) +
  aes(x = green_tot_pomp ,
      y = comp_tot_pomp ,
      fill = student ,
      color = student) +
  geom_jitter(alpha = .4, height = .5, width = .5) +
  # geom_smooth(data = subset(ng_data, student == "NonStudent"| student == "student")) # BMW: This doesn't product separate lines by group. Is that what you were trying to do? See below. 
  geom_smooth() +
  # geom_smooth(color = "black", fill = "black") # BMW: If you wanted one line for the whole sample, but separately by group is better here.
  
ggplot(na.omit(ng_data)) +
  aes(x = green_tot_pomp ,
      y = open_tot_pomp ,
      fill = student ,
      color = student) +
  geom_point() +
  geom_smooth()

ggplot(na.omit(ng_data)) +
  aes(x = green_tot_pomp,
      y = intel_tot_pomp,
      fill = student ,
      color = student) +
  geom_point() +
  geom_smooth() 
```  

The rainfall plots show that students had slightly higher scores than non-students across the measures, however no-students seemed to have higher scores regarding green reputation


  6. Compare **green reputation** for students and non-students using a **rainfall plot** (bar + density + data points).
  
```{r , rainfall plot}
ggplot(na.omit(ng_data)) +
  aes(x = green_tot_pomp ,
      y = student ,
      color = student) +
  geom_jitter(height = .20) +
  geom_boxplot(
    color = "violet",
    alpha = .5 ,
    width = .1 ,
    size = .5
  ) +
  ggdist::stat_slab(
    height = .3,
    color = "green",
    size = .2 ,
    alpha = .5 ,
    position = position_nudge(y = .1)
  )
```


This plot sows that students seem to have lower green reputation scores than non-students.


  7. Compute a summary table of means, SDs, medians, minima, and maxima for the four total scores for students and non-students.
  
```{r final summary}
ng_data %>%
  group_by(student) %>%
  summarize(across(
    c(green_tot_pomp, comp_tot_pomp, intel_tot_pomp, open_tot_pomp),
    list(
      mean = ~ mean(.x , na.rm = TRUE),
      SD = ~ sd(.x , na.rm =  TRUE),
      median = ~ median(.x , na.rm =  TRUE),
      minima = ~ min(.x, na.rm =  TRUE),
      mxima = ~ max(.x, na.rm = TRUE)
    )
  ))
``` 

The summary shows that non-students score slightly higher than students in total measures of green,comp, intel, but not in the open measure. 
In regards to standar deviation, non-students was lower than for students in the green, intel, and open measures, however, it was higher for the comp measure.
The median of green, and comp measures, however, the medians for open, and intel were similar.   
Maximas were similar amongst students and non-students for green,but the scores were higher for students in the measures of intel, and open. 
Finally, for the minimas, the scores were higher for non-students across all measures. 

In your assignment, prepare an RMarkdown file that includes both the coding and (for 4-7) narrative descriptions of your results.
