# Homework 03

You will analyze data looking at the relationship between **green reputation** and three personality traits--**compassion**, **intellectual curiosity**, and **openness to experiences**.
The dataset includes data from **students** and **non-students**.

```{r}
dictionary <- readr::read_csv("green_dictionary.csv")
green_data <- readr::read_csv("green_data.csv")
library(dplyr) 
library(ggplot2)
library(tidyverse)
``` 

For your assignment, do the following.

  1. Inspect the item responses (e.g., with graphs or by summarizing distinct values). 
     Is anything unusual?
```{r}
summary(green_data) 

```
  
 
  2. Compute total scores for the four scales. 
     Recode variables as needed.
```{r}
green_data %>%
mutate(
  across(eeverything(),
 ~ recode(.x , "-99" = NA, .default = .x)
))

#   ~ says that you are going to use the .x symbol , .x marks the spot 
# 'everything()' = ALL COLUMNS 
# .missing is for when you look for missing values 
# NA is for when this is missing 
# .x = the current column 

```   
  
  
  3. Rescale the variables so that they go from 0-100 instead of the original range.
     Name the rescaled variables `*_pomp`.
```{r}
reversed <- c("green1", "green2","green3", "green4", 
              "green5" , "comp1", "comp2", "comp3", 
              "comp4", "comp5", "comp6", "comp7", "comp8", "comp9", "comp10", 
              "intel1", "intel2", "intel3", "intel4", "intel5", "intel6",
              "intel7", "intel8", "intel9", "intel10", "open1",
              "open2", "open3", "open4", "open5", "open6", "open7", "open8",
              "open9", "open10")
new_green_data <- green_data %>% 
                    mutate(
                           across(all_of(reversed),
                           ~ recode(.x, "1" = 0, "2" = 25, "4" = 75, "5" = 100)
                          )) %>% 
  rowwise() %>% 
  mutate(green_pomp = sum(c
                         (green1,green2,green3,green4,green5), na.rm = TRUE),
         comp_pomp = sum(c
                        (comp1,comp2,comp3,comp4,comp5,comp6,comp7,comp8,comp9,comp10), na.rm = TRUE),
         intel_pomp = sum(c
                         (intel1,intel2,intel3,intel4,intel5,intel6,intel7,intel8,intel9,intel10), na.rm = TRUE),
         open_pomp = sum(c
                        (open1,open2,open3,open4,open5,open6,open7,open8,open9,open10), na.rm = TRUE),) 

```
 
 
 
 
  4. Make plots that illustrate the distributions of the 4 POMP-scored variables.
  
```{r}
ggplot(new_green_data) +
  aes(x = green_pomp) +
  geom_histogram( fill = "pink")+
  theme_classic()

ggplot(new_green_data) +
  aes(x =intel_pomp) +
  geom_histogram(fill = "green")+
  theme_classic()

ggplot(new_green_data) +
  aes(x = comp_pomp) +
  geom_histogram(fill = "blue")+
  theme_classic()

ggplot(new_green_data) +
  aes(x = open_pomp) +
  geom_histogram(fill = "purple")+
  theme_classic()

```  
  
  
  
  5. Make scatterplots showing the relationships between **green reputation** and each personality trait.
     Include trend lines for **students** and **non-students**.
     What do these plots show?
```{r}

new_green_data %>%
  mutate(
    student = recode(student , "1" = "Student" , "2" = "NonStudent")
  )

ggplot(na.omit(new_green_data)) +
  aes( x = green_pomp ,
       y = comp_pomp ,
       fill = student , 
       color = student) +
  geom_point() +
  geom_smooth(data = subset(new_green_data , student == "NonStudent" 
                            | student == "student"))

ggplot(na.omit(new_green_data)) +
  aes( x = green_pomp ,
       y = open_pomp ,
       fill = student , 
       color = student) +
  geom_point() +
  geom_smooth(data = subset(new_green_data , student == "NonStudent" 
                            | student == "student"))

ggplot(na.omit(new_green_data)) +
  aes( x = green_pomp ,
       y = intel_pomp ,
       fill = student , 
       color = student) +
  geom_point() +
  geom_smooth(data = subset(new_green_data , student == "NonStudent" 
                            | student == "student"))
```  
  
  
  
  6. Compare **green reputation** for students and non-students using a **rainfall plot** (bar + density + data points).
```{r}

ggplot(na.omit(new_green_data)) +
  aes( x = student , 
       y = green_pomp , 
       color = student) +
  geom_jitter( height = .20)+
  geom_boxplot(color = "green",
               alpha = .5 ,
               width = .1 , 
               size = .5 ) +  
  ggdist::stat_slab(
                    height = .3,
                    color ="green",
                    size = .2 ,
                    alpha = .5 ,
                    position = position_nudge( y = .5)
                    )
```
 
 
 
 
 
  7. Compute a summary table of means, SDs, medians, minima, and maxima for the four total scores for students and non-students.
```{r}

``` 
 
  
In your assignment, prepare an RMarkdown file that includes both the coding and (for 4-7) narrative descriptions of your results.
