---
title: "HW_3"
author: "Antonietta"
date: "2/23/2021"
output: 
gitthub_document: default 
    html_document: default 
    keep_md: TRUE

---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(dplyr) 
library(ggplot2)
library(tidyverse)
library(scales)

```

# Homework 03

You will analyze data looking at the relationship between **green reputation** and three personality traits--**compassion**, **intellectual curiosity**, and **openness to experiences**.
The dataset includes data from **students** and **non-students**.

```{r}
dictionary <- readr::read_csv("green_dictionary.csv")
green_data <- readr::read_csv("green_data.csv")

``` 

For your assignment, do the following.

  1. Inspect the item responses (e.g., with graphs or by summarizing distinct values). 
     Is anything unusual?
```{r}
print(green_data)  #The -99 isunusual 

new_green_data <- green_data %>%
mutate(
  across(everything(),
 ~ na_if(.x , "-99")), 
 student = recode(student, "1" = "not a student", "2" = "student", .missing = "Unknown"))

 #The min. value of -99 is now replaced with 1, and all the -99 are NA 

summary(new_green_data) 

#   ~ says that you are going to use the .x symbol , .x marks the spot 
# 'everything()' = ALL COLUMNS 
# .missing is for when you look for missing values 
# NA is for when this is missing 
# .x = the current column 
```


  2. Compute total scores for the four scales. 
     Recode variables as needed.
```{r}

#We will be recoding variables to make them more concrete and easier to read 

ng_data <- new_green_data %>%
  rowwise() %>% 
  mutate(green_tot = sum(c(green1,green2,green3,green4,green5), na.rm = FALSE),
         comp_tot = sum(c(comp1,comp2,comp3,comp4,comp5,comp6,comp7,comp8,comp9,comp10), na.rm = FALSE),
         intel_tot = sum(c(intel1,intel2,intel3,intel4,intel5,intel6,intel7,intel8,intel9,intel10), na.rm =FALSE),
         open_tot = sum(c(open1,open2,open3,open4,open5,open6,open7,open8,open9,open10), na.rm = FALSE)
   )

print(ng_data
      )

```   


  3. Rescale the variables so that they go from 0-100 instead of the original range.
     Name the rescaled variables `*_pomp`.
```{r}

ng_data <- ng_data %>% 
   mutate(across
          (c(green1:open10),
             ~ recode(.x, "1" = 0, "2" = 25, "3" = 50, "4" = 75, "5" = 100),
                           .names = "{.col}_pomp")
                          ) 
  ng_data <- ng_data %>% 
  rowwise() %>% 
  mutate(
    green_tot_pomp = mean(
      c_across(green1_pomp:green5_pomp), na.rm = TRUE),
    comp_tot_pomp = mean(
           c_across(comp1_pomp:comp10_pomp), na.rm = TRUE),
    intel_tot_pomp = mean(
           c_across(intel1_pomp:intel10_pomp), na.rm = TRUE),
    open_tot_pomp = mean(
           c_across(open1_pomp:open10_pomp), na.rm = TRUE),)
 
```




  4. Make plots that illustrate the distributions of the 4 POMP-scored variables.

```{r}
ggplot(ng_data) +
  aes(green_tot_pomp) +
  geom_histogram( binwidth = 5, 
                  fill = "pink" , 
                  col = "black")+
  theme_classic()

ggplot(ng_data) +
  aes(intel_tot_pomp) +
  geom_histogram(binwidth = 5 , fill = 
                   "orange", 
                 col = "black")+
  theme_classic()

ggplot(ng_data) +
  aes(comp_tot_pomp) +
  geom_histogram(binwidth = 5, 
                 fill = "cyan", 
                 col = "black")+
  theme_classic()
  
ggplot(ng_data) +
  aes(open_tot_pomp) +
  geom_histogram(binwidth = 5,
                 fill = "violet", 
                 col = "black")+
  theme_classic()
```  

The histograms show that all the variables are roughly normally distributed. The green vaiable seems to be positively skewed. 



  5. Make scatterplots showing the relationships between **green reputation** and each personality trait.
     Include trend lines for **students** and **non-students**.
     What do these plots show?
```{r}

ggplot(na.omit(ng_data)) +
  aes( x = green_tot_pomp ,
       y = comp_tot_pomp ,
       fill = student , 
       color = student) +
  geom_point() +
  geom_smooth(data = subset(ng_data, student == "NonStudent" 
                            | student == "student"))
ggplot(na.omit(ng_data)) +
  aes( x =green_tot_pomp ,
       y = open_tot_pomp ,
       fill = student , 
       color = student) +
  geom_point() +
  geom_smooth(data = subset(ng_data , student == "NonStudent" 
                            | student == "student"))
ggplot(na.omit(ng_data)) +
  aes( x = green_tot_pomp ,
       y = intel_tot_pomp ,
       fill = student , 
       color = student) +
  geom_point() +
  geom_smooth(data = subset(ng_data , student == "NonStudent" 
                            | student == "student"))
```  

The rainfall plot 


  6. Compare **green reputation** for students and non-students using a **rainfall plot** (bar + density + data points).
```{r}
ggplot(na.omit(ng_data)) +
  aes( x = green_tot_pomp , 
       y = student , 
       color = student) +
  geom_jitter( height = .20)+
  geom_boxplot(color = "violet",
               alpha = .5 ,
               width = .1 , 
               size = .5 ) +  
  ggdist::stat_slab(
                    height = .3,
                    color ="green",
                    size = .2 ,
                    alpha = .5 ,
                    position = position_nudge( y = .5)
                    )
```


This plot sows that students seem to have lower green reputation scores than non-students.


  7. Compute a summary table of means, SDs, medians, minima, and maxima for the four total scores for students and non-students.
```{r}

ng_data %>%
  group_by(student) %>%
  summarize(across(c(green_tot_pomp, comp_tot_pomp, intel_tot_pomp, open_tot_pomp),
            list(
              mean = ~mean(.x , na.rm = TRUE),
              SD = ~sd(.x , na.rm =  TRUE), 
              median = ~median(.x , na.rm =  TRUE),
              minima = ~min(.x, na.rm =  TRUE), 
              mxima = ~max(.x, na.rm = TRUE)
            )))

``` 

The summary shows that non-students score slightly higher than students in total measures of green,comp, intel, but not in the open measure. 
In regards to standar deviation, non-students was lower than for students in the green, intel, and open measures, however, it was higher for the comp measure.
The median of green, and comp measures, however, the medians for open, and intel were similar.   
Maximas were similar amongst students and non-students for green,but the scores were higher for students in the measures of intel, and open. 
Finally, for the minimas, the scores were higher for non-students across all measures. 

In your assignment, prepare an RMarkdown file that includes both the coding and (for 4-7) narrative descriptions of your results.