---
title: "Beer Advocate: ABV and quality ratings"
author: "Your Name Here"
output: html_document
---

# CLASS NOTES 3/4/21

To control column types, use 'cols()' function 
e.g.

```{r , eval = FALSE}
data <- read_csv(
here::here("participation", "data", "gap_asia_2007"),
cols(
country = col_character(),
continent = col_character(), 
year = col_double(),
pop = col_double(),
gdpPercap = col_double(),
.default = col_double() #sets all other columns to double 
),
na = c("", "NA", -99, "No response") #make those missing 
)
```

SAVING 

```{r , eval = FALSE}

write.csv(
  clevel_cleaned, #what we are saving
  here::here("participation", "data", "clevel_cleaned.csv")
) #where we are saving it to and with what name
```



PLOTS
```{r , eval = FALSE}
dir.create(here::here("participation","output","figures"). recursive = TRUE)
ggsave(here::here()

```



# ACTIVITY

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
```

For this activity, download the data file at this location to the `data` subfolder in your `participation` folder. 
This dataset contains information about different catagories of beer as rated on <beeradvocate.com>.
The data are originally from [here](http://scottjanish.com/relationship-of-abv-to-beer-scores/).

The dataset contains 3 variables:

  1. Beer category
  2. Average alcohol by volume (ABV) in percentage (%)
  3. Average quality rating (rAVG) on a 1–5 scale
  
You should write a script to do the following:



 1. Download the dataset with an appropriate filename.


 
```{r}


if( !dir.exists(here::here("participation","data"))) {
  dir.create(here::here("participation","data"), recursive =TRUE)
}


url <- "https://raw.githubusercontent.com/USF-Psych-DataSci/Classroom/master/data/beer-advocate.csv" 
download.file(url, 
              here::here("participation",
                         "data","beerdata.csv"),
              mode= "wb"                                                     )

```


 2. Import the dataset into R.

```{r}

beerdata <- read_csv(
  here::here("participation","data", "beerdata.csv"),
  col_types = cols(
    'Beer Category' = col_character(),
    'Average ABV' = col_double(),
    'rAVG' = col_double()
  ), 
  na = c("", "NA", "Non-alcoholic")
  )

#control i = reindents
#always use read_csv because it tells you the sort of data 
#na = helps you not read / read as NA 
```


 
  3. Make a figure illustrating the relationship between ABV and beer quality.

```{r, eval = FALSE}

beerdata %>%
  ggplot() +
  aes(x = `Average ABV`,
      y = `rAVG`)+
  geom_point(fill = `Average ABV` ,
      color = `Average ABV`,
      alpha = .5,
      size = 2, 
      shape = 20) +
  stat_smooth(method = lm)+
  theme_classic()

```
     Be sure to check for any importing problems and correct as needed.
  
  
  4. Compute a summary table with the mean and SD of each variable, along with their correlation.
  
```{r}
beerdata %>%
  summarise(across(c(`Average ABV`, rAVG),
            list(
              mean = ~mean(.x, na.rm = TRUE),
              SD = ~sd(.x , na.rm =  TRUE))))

cor.test(`Average ABV`, rAVG, method = c("Average ABV", "rAVG"))

```
  
  5. Describe the results.
  
  
